The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society

### 2023-11-28 manuscript/manuscript.qmd
Strike out the organizational flexibility stuff in the intro
Eventually this whole paragraph will match the rest of the paper, once the rest of the paper is more done

TODO: Andrew: Roadmap of paper, to add later
In this paper, we first explore the ongoing phenomena of closing civic space and authoritarian regulation of civil society, examining how governments conceptualize the role of international civil society in their domestic politics and why governments select regulatory regimes for international NGOs. We then investigate how international NGOs have responded and adapted to more restrictive regulatory environments and theorize that a key component of INGO regulatory adaptation is *organizational flexibility*, or the ability to operate with greater latitude in host countries. We propose two key determinants of this flexibility: (1) organizational characteristics and (2) host government preferences and relationships TODO and their interplay/interaction. We illustrate this theory using the case of China TODO stats and case studies, mixed method, demonstrating how INGOs that address issues that align with government preferences enjoy the most organizational flexibility in the country.

>>>>

TODO: Andrew: Roadmap of paper, to add later
In this paper, we first explore the ongoing phenomena of closing civic space and authoritarian regulation of civil society, examining how governments conceptualize the role of international civil society in their domestic politics and why governments select regulatory regimes for international NGOs. ~~We then investigate how international NGOs have responded and adapted to more restrictive regulatory environments and theorize that a key component of INGO regulatory adaptation is the ability to operate with greater latitude in host countries. We propose two key determinants of this flexibility: (1) organizational characteristics and (2) host government preferences and relationships TODO and their interplay/interaction.~~ We illustrate this theory using the case of China TODO stats and case studies, mixed method, demonstrating how INGOs that address issues that align with government preferences enjoy the most organizational flexibility in the country.
